---
title: "Old Faithful"
format: html
server: shiny
---

## this is just for illustration 

```{r}
sliderInput("bins", "Number of bins:", 
            min = 1, max = 50, value = 30)
plotOutput("distPlot")
```

```{r}
#| context: server
output$distPlot <- renderPlot({
  x <- faithful[, 2]  # Old Faithful Geyser data
  bins <- seq(min(x), max(x), length.out = input$bins + 1)
  hist(x, breaks = bins, col = 'darkgray', border = 'white')
})
```

## Introduction

In this analysis, we build a model predicting sale prices of houses based on data on houses that were sold in the Duke Forest neighborhood of Durham, NC around November 2020. Let's start by loading the packages we'll use for the analysis.

```{r, warning=FALSE}
#| label: load-pkgs
#| code-summary: "Packages"
#| message: false

library(openintro)  # for data
library(tidyverse)  # for data wrangling and visualization
library(knitr)      # for tables
library(broom)      # for model summary
```

We present the results of exploratory data analysis in @sec-eda and the regression model in @sec-model.

We're going to do this analysis using literate programming [@knuth1984].

## Exploratory data analysis {#sec-eda}

The data contains `r nrow(duke_forest)` houses. As part of the exploratory analysis let's visualize and summarize the relationship between areas and prices of these houses.

### Data visualization

@fig-histogram shows two histograms displaying the distributions of `price` and `area` individually.

```{r}
#| label: fig-histogram
#| fig-cap: "Histograms of individual variables"
#| fig-subcap:
#|   - "Histogram of `price`s"
#|   - "Histogram of `area`s" 
#| layout-ncol: 2
#| column: page-right

ggplot(duke_forest, aes(x = price)) +
  geom_histogram(binwidth = 50000) +
  labs(title = "Histogram of prices")

ggplot(duke_forest, aes(x = area)) +
  geom_histogram(binwidth = 250) +
  labs(title = "Histogram of areas")
```
